\documentclass[11pt,a4paper,sans]{moderncv}% possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 
\moderncvstyle{classic} % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'

\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{} % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage[utf8]{inputenc} % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage[scale=0.75]{geometry}
\usepackage{ragged2e}

\name{José Jair}{Santanna}
\title{Application letter}                               
\address{University of Twente}{Drienerlolaan 5\\7522 NB Enschede}{The Netherlands}
\phone[mobile]{+31~(53)~4892505}                   
\email{j.j.santanna@utwente.nl}                             
\homepage{www.jairsantanna.com}                     


\begin{document}

% To whom is the letter?
\recipient{ass}{as}
\date{\today} % Date of today
% Opening
\opening{Dear Sir or Madam,}
% Closing
\closing{Yours faithfully,}

\makelettertitle

\justify
I am delighted to notice that I have both the characteristic of your \textit{ideal
candidate} and the \textit{essential qualifications} that you are looking for.
Therefore, I would appreciate if you to consider my application. The remaining
of this letter describes how do I meet your requirements and how do I plan my
academic career in a short and long-term.

\textbf{Educational records}. In 2012 I had a great experience to be
\textit{assistant professor} in the University of Santa Cruz do Sul, Brazil.
Back there I taught 'digital systems', 'computer networks' and 'network
management' to bachelors in computer science. In Brazil the doctor degree is not
a requirement to have a position of assistant professor. In the last couple of
years I had the opportunity to be \textit{guest lecturer} at our university
(University of Twente - UT) in the courses 'product design to online business'
(module), 'network management', 'network security' and 'cybercrime \&
cybersecurity'(minor). I would like to emphasize my passion for teaching, which
is clearly noticed by the students\footnote{In the end of the last couple of
lectures I ask students to voluntarily judge my lecture. The result is available
at
\url{https://docs.google.com/forms/d/1DHextGLTfdNc3Gsu1BVYlviqObwOnpV2LDJwLQCgz3A/viewanalytics?usp=form_confirm}}
that I had pleasure to teach and judge me as an enthusiastic teacher (88.9\%)
giving a a ``fun'' lecture (94.4\%). 

\textbf{Research records}. Let me first say that the general quality level of
publications naturally improves along an academic career. My main publications
were published in conferences with the highest indices I am eager publication
when I was in the.  Capacity to develop something useful.  I am preparing one of
the last submiti John Heidmann ACM SIGCOMM

% Educational (teaching) records
- I have a lot of pleasure giving lecture and I very positive feedback from
students. In the last lectures (i.e., network management \& SNMP v1,2 and 3;
cyber security; cyberSecurity \& DDoS attacks). 18 students
OOC \footnote{\url{https://www.youtube.com/watch?v=kBBIqKeVdDo}}.  I have passion to do it. The best part is that my audience notice it on
me.  i

% Research track records

I am very excited with the position offered for many reasons. Firstly, I follow
the work developed at RIPE NCC and admire your entrepreneurship on making
available one of the biggest network data infrastructures worldwide. Secondly, I
do not only use the RIPE atlas and RIPEstat infrastructure, but helped spreading
the deployment of probes in regions where RIPE did not yet have access (e.g.,
the north part of Brazil). I also gave training to students preparing them to
explore your valuable infrastructure. A successful collaboration with a student,
in which we use thousands of RIPE Atlas probes, was awarded as the best paper at
an international academic conference (AIMS 2015). We also presented the results
of this collaboration at the plenary session of RIPE meeting 69.

Besides my enthusiasm and the fact that I already like to live in the
Netherlands (except for the weather), I am glad to observe that I attend all the
general, essential and desirable qualifications described for the position. To
facilitate your judgment I made the achievement of the required qualifications
explicit over my CV. On top of that, the description of your ``ideal applicant''
(i.e., focus on prototyping tools, analysing network data, and publishing
reports) is exactly what I have done during the last years as a PhD researcher.
For example, I developed a prototype to generate an unique and valuable type of
blacklist (\url{http://booterblacklist.com}). The output of my prototype has
been used since June 2016 at the Dutch academic network (SURFnet) to monitor a
serious cyberthreats in the Dutch society. The analysis of one year of SURFnets
monitored data (DNS-based) is available at
\url{https://github.com/jjsantanna/booterblacklist_surfnet_case}. All the
description of our prototype and results achieved were submitted to a well
ranked international academic conference, and it is under reviewing process.

Finally, I am currently in the last year of my PhD at the University of Twente,
and I am certain that working as a Researcher at RIPE would be a great way to
continue my career as a network researcher engineer and a (big) data analyst.
Thank you for taking the time to consider this application and I look forward to
hearing from you in the near future.

% Career Goal
\textbf{Career goals}. (1) Develop
recognized by the scientific community 
(2) Lead
(3) Enforce and complement the name of the institution in which I work with.


% Career Planning
\textbf{Career Planning}. Enthusiastic independent researcher. During my master
I decidedAs I have decided to follow the academic carrier my first steps was to
plan where I want to publish, in which community I want to be known, how can I
keep my work founded 	Research
grants\footnote{\url{https://docs.google.com/spreadsheets/d/1ugeipC-5f6Ggf0q4TGvLK2N47DC0KEehdW7AgOQyTKM/edit?usp=sharing}}
and paper
submission\footnote{\url{https://github.com/jjsantanna/research_grants_planning/blob/master/research_grants_planning.ipynb}} 


% Collaborations

\makeletterclosing

\end{document}
