\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{José Jair }{Cardoso de Santanna}{Ph.D. Researcher, Lecturer, Network Security Specialist \& (Big) Data Analyst} 

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
Mooienhof 10-45
7512EB Enschede
The Netherlands
~
+31 (6) 42330703
~
\href{mailto:j.j.santanna@utwente.nl}{j.j.santanna@utwente.nl}
\href{http://jairsantanna.com}{http://jairsantanna.com}
\href{https://www.linkedin.com/in/jjcsantanna}{linkedin: jjcsantanna}
\section{Languages}
portuguese native 
english fluency
spanish comprehension
dutch comprehension
\section{Programming}
Bash, Python, C\#,SQL
{\color{green} $\varheartsuit$} PIG, Spark \& Impala
\end{aside}


\section{Education}

\begin{entrylist}
\entry
{2013--Now}
{Doctor}
{University of Twente, The Netherlands}
{\emph{The DDoS as a \$ervice Phenomenon} \\ 
This thesis ...}	

\entry
{2010--2012}
{Master {\normalfont in Computer Science}}
{Federal University of Rio Grande do Sul, Brazil}
{\emph{A BPM-based Solution for Inter-domain Circuit Management.} \\ 
This thesis explored the idea ...}

\entry
{2005--2010}
{Bachelor {\normalfont in Computer Engineer}}
{Federal University of Par\'a, Brazil}
{\emph{Comparative Evaluation of DCCP Protocol in a Experimental Mesh Network.} \\ 
This dissertation ...}

\end{entrylist}

\section{Experience}

\subsection{Assistant Professor}
\begin{entrylist}
\entry
{2012--2013}
{University of Santa Cruz do Sul (UNISC)}
{Santa Cruz do Sul, Brazil}
{\emph{1\textsuperscript{st} Year Analyst}
\begin{itemize}
\item Computer Networks;
\item Computer Network Management;
\item Digital Systems.
\end{itemize}}
\end{entrylist}

\subsection{Guest Lecturer}
\begin{entrylist}
\entry
{2015 \& 2016}
{University of Twente}
{Enschede, The Netherlands}
{\emph{Course: Product Design to Online Business}\\ 
Audience: bachelor students of industrial engineering and business information technology. 
}

\entry
{2015}
{University of Twente}
{Enschede, The Netherlands}
{\emph{Course: Network Security}\\ 
Audience: master and bachelor students of computer science and electrical engineer, master students of computer science and telematics, master students from the 3TU cyber security, and members of ICT labs. 
}

\entry
{2015}
{University of Twente}
{Enschede, The Netherlands}
{\emph{Course: Minor in Cybercrime \& Cybersecurity}\\ 
Audience: bachelor students from University of Twente, European Research Center for Information (ERCIS), Westfälische Wilhelms - Univerität Münster, Universität Innsbruck, and University of Leicester.  
}
\end{entrylist}

\subsection{Software Developer}
\begin{entrylist}
\entry
{2010--2011}
{Brazilian National Education and Research Network (RNP)}
{Rio Grande do Sul, Brazil}
{Development of a online tool to \emph{Create, Edit and Execute Management Networks Policies (MEICAN).}\\
Language: WS-BPEL
}

\entry
{2009}
{Scholarship Students of Scientific Initiation}
{Federal University of Pará, Brazil}
{Development of a desktop application to \emph{Support the Sustainable Electrical Power Generation Planning using Vegetable Oil.} The system was used as part of the Ph.D. thesis of Prof. Dr. Ana Rosa Carriço de Lima Montenegro Duarte.\\
Language: C\#.Net \& mySQL
}
\end{entrylist}

%\subsection{Data Analyst}
%\begin{entrylist}
%\entry
%{2010--2011}
%{LEHMAN BROTHERS}
%{London, United Kingdom}
%{\emph{Summer Intern} \\
%Received pre-placed offer from the Exotics Trading Desk as a result of very positive reviews. Rated "truly distinctive" for Analytical Skills and Teamwork.}
%\end{entrylist}

\subsection{Student Supervisor}
\begin{entrylist}
\entry
{2010--2011}
{LEHMAN BROTHERS}
{London, United Kingdom}
{\emph{Summer Intern} \\
Received pre-placed offer from the Exotics Trading Desk as a result of very positive reviews. Rated "truly distinctive" for Analytical Skills and Teamwork.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

\begin{entrylist}
\entry
{2015}
{Best Ph.D. 'Elevator Pitch' (1$^{st}$ Place)}
{CTIT Symposium, University of Twente}

\entry
{2015}
{Best Poster (3$^{rd}$ Place)}
{CTIT Symposium, University of Twente}

\entry
{2015}
{Best Paper Award}
{Autonomous Infrastructure, Management and Security Conference}

\entry
{2015}
{Top Papers Nomination}
{Brazilian Symposium on Computer Networks and Distributed Systems}

\entry
{2010}
{Student Award (3$^{rd}$ Place)}
{Computer Engineer, Federal University of Pará, Brazil}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Communication Skills}
\emph{More than 50 presentations only during the period of Ph.D. researcher.}

\begin{entrylist}

\entry
{2015}
{Oral Presentation}
{at Logius (part of the Dutch Ministry of the Interior and Kingdom Relations).}

\entry
{2015}
{Oral Presentation}
{to the Dutch National Management Organization of Internet Providers (NBIP).}

\entry
{2015}
{Oral Presentation}
{to the Dutch National Cyber Security Centrum (NCSC).}

\entry
{2013 \& 2015}
{Oral Presentation}
{at the 31$^{th}$ and 36$^{th}$ IRTF Network Management Research Group (NMRG).}

\end{entrylist}

\section{Interests}
\textbf{Professional:} data analysis, company profiling, risk analysis, economics, web design, web app creation, software design, marketing\\ \\ \textbf{Personal:} crosfit, running, cooking, dancing, traveling

\section{Publications}
\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography

\printbibsection{book}{books} % Print all books from the bibliography

\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
\nocite{*}
\printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=bibheading]
\end{refsection}

\begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing "keyword=france"
\nocite{*}
\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=bibheading]
\end{refsection}

\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography

\printbibsection{report}{research reports} % Print all research reports from the bibliography

\end{document}