\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 
\moderncvstyle{classic}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'

%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage[scale=0.75]{geometry}
\usepackage{ragged2e}


\name{José Jair}{Santanna}
\title{Cover letter}                               
\address{Mooienhof 10, 45}{7512EB Enschede}{The Netherlands}
\phone[mobile]{+31~(6)~42330703}                   
\email{jairsantanna@gmail.com}                             
\homepage{www.jairsantanna.com}                     



\begin{document}
\recipient{RIPE NCC}{Réseaux IP Européens Network Coordination Centre \\Singel 258, 1016 AB\\Amsterdam}
\date{\today}
\opening{Dear Sir or Madam,}
\closing{Yours faithfully,}

\makelettertitle

\justify
Please find enclosed my CV in application for the Job Reference Number 2016-007.

I am very excited with the position offered for many reasons. Firstly, I follow the work developed at RIPE NCC and admire your entrepreneurship on making available one of the biggest network data infrastructures worldwide. Secondly, I do not only use the RIPE atlas and RIPEstat infrastructure, but helped spreading the deployment of probes in regions where RIPE did not yet have access (e.g., the north part of Brazil). I also gave training to students preparing them to explore your valuable infrastructure. A successful collaboration with a student, in which we use thousands of RIPE Atlas probes, was awarded as the best paper at an international academic conference (AIMS 2015). We also presented the results of this collaboration at the plenary session of RIPE meeting 69.

Besides my enthusiasm and the fact that I already like to live in the Netherlands (except for the weather), I am glad to observe that I attend all the general, essential and desirable qualifications described for the position. To facilitate your judgment I made the achievement of the required qualifications explicit over my CV. On top of that, the description of your ``ideal applicant'' (i.e., focus on prototyping tools, analysing network data, and publishing reports) is exactly what I have done during the last years as a PhD researcher. For example, I developed a prototype to generate an unique and valuable type of blacklist (\url{http://booterblacklist.com}). The output of my prototype has been used since June 2016 at the Dutch academic network (SURFnet) to monitor a serious cyberthreats in the Dutch society. The analysis of one year of SURFnets monitored data (DNS-based) is available at \url{https://github.com/jjsantanna/booterblacklist_surfnet_case}. All the description of our prototype and results achieved were submitted to a well ranked international academic conference, and it is under reviewing process.

Finally, I am currently in the last year of my PhD at the University of Twente, and I am certain that working as a Researcher at RIPE would be a great way to continue my career as a network researcher engineer and a (big) data analyst. Thank you for taking the time to consider this application and I look forward to hearing from you in the near future.


\makeletterclosing

\end{document}


%% end of file `template.tex'.
